Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-03-08 Methods-and-Results.Rmd
code display fix

```{generalForestPltComb}
effGeneral <- rbind(
  eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Aggregate Linear Regression",
           metaId = paste(coef, analysis, sep = ".")),
  GeneralLmerMeta$eff %>%
    mutate(analysis = "(B) Mixed Effects Regression",
           metaId = paste(coef, analysis, sep = "."))
)

@@

```{theoryForestPltComb}
effTheory <- rbind(
  TheoryMetaQualityNeed$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Quality ~ Core Need",
           metaId = paste(coef, analysis, sep = ".")),
  TheoryMetaAttitudeNeed$eff %>%
    mutate(analysis = "(B) Attitude ~ Core Need",
           metaId = paste(coef, analysis, sep = ".")),
  TheoryMetaAttitudeNeedQuality$eff %>%
    mutate(analysis = "(C) Attitude ~ Core Need + Quality",
           metaId = paste(coef, analysis, sep = "."))
)

@@

```{robustForestPltComb}
effRobust <- rbind(
  robustMetaContact$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Contact and Need Fulfillment",
           metaId = paste(coef, analysis, sep = ".")),
  robustMetaSDT$eff %>%
    mutate(analysis = "(B) Other Needs",
           metaId = paste(coef, analysis, sep = "."))
)

>>>>

```{generalForestPltComb, include=FALSE}
effGeneral <- rbind(
  eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Aggregate Linear Regression",
           metaId = paste(coef, analysis, sep = ".")),
  GeneralLmerMeta$eff %>%
    mutate(analysis = "(B) Mixed Effects Regression",
           metaId = paste(coef, analysis, sep = "."))
)

@@

```{theoryForestPltComb, include=FALSE}
effTheory <- rbind(
  TheoryMetaQualityNeed$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Quality ~ Core Need",
           metaId = paste(coef, analysis, sep = ".")),
  TheoryMetaAttitudeNeed$eff %>%
    mutate(analysis = "(B) Attitude ~ Core Need",
           metaId = paste(coef, analysis, sep = ".")),
  TheoryMetaAttitudeNeedQuality$eff %>%
    mutate(analysis = "(C) Attitude ~ Core Need + Quality",
           metaId = paste(coef, analysis, sep = "."))
)

@@

```{robustForestPltComb, include=FALSE}
effRobust <- rbind(
  robustMetaContact$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Contact and Need Fulfillment",
           metaId = paste(coef, analysis, sep = ".")),
  robustMetaSDT$eff %>%
    mutate(analysis = "(B) Other Needs",
           metaId = paste(coef, analysis, sep = "."))
)
